\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage[utf8]{inputenc}
\usepackage{enumitem}

    


% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Custom commands
\begin{document}
\include{custom-commands}

%-------------------------------------------%
%%%%%%  RESUME STARTS HERE  %%%%%

%----------HEADING----------%
\begin{center}
    \textbf{\Huge \scshape Deena Swaminathan K} \\ \vspace{8pt}
    \textbf{\Large \scshape Bus \& Technology Delivery Senior Analyst} \\ \vspace{4pt}
    \small Bengaluru, Karnataka \textbar\ 
    \small +91 8838849720 \textbar\ 
    \href{mailto:dheenakumar107@gmail.com}{{\small dheenakumar107@gmail.com}} \textbar\ 
    \href{https://www.linkedin.com/in/deena-swaminathan-k-0893179a/}{{\small LinkedIn}} \textbar\ 
    \href{https://github.com/DeenaSwaminathanKumaravel}{{\small Github}} \textbar\ 
    \href{https://www.hackerrank.com/profile/dheenakumar107}{{\small HackerRank}} \textbar\ 
    \href{https://public.tableau.com/app/profile/deena6901/vizzes}{{\small Tableau Public}}
\end{center}

%-----------SUMMARY-----------%
\section{Summary}
    \begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{Analytical professional with 8 years of experience in project management, ML algorithms, business development, and business intelligence. Expertise in generating insightful reports, predictive models, and dynamic visualizations.}}
    \end{itemize}


%-----------TECHNICAL SKILLS-----------%
\section{Technical Skills}
\begin{itemize}[leftmargin=0.35in, label=\textbullet, itemsep=0.0em]
    \item \small \textbf{Scripting Languages}: Python, VBA
    \item \small \textbf{Database Languages}: MYSQL, PostgreSQL, MS SQL Server
    \item \small \textbf{Data Visualization}: Tableau, Power BI
    \item \small \textbf{Statistical Concepts}: Predictive Analytics, Hypothesis, ANOVA, Text Analytics, EDA
    \item \small \textbf{UI/UX Design}: Figma
    \item \small \textbf{ETL Tools}: Tableau Prep, Alteryx, KNIME
    \item \small \textbf{Others}: MS Fabric, MS Azure, Advanced Excel, Power Apps, Dbeaver, Power Automate, Six Sigma, Problem Solving, Communication
\end{itemize}


%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Accenture}{Mar 2019 -- Present}
    {Bus \& Technology Delivery Senior Analyst}{Bengaluru, Karnataka}
    \resumeItemListStart
        \resumeItem{Created new reports using SQL and modified existing dashboards, drill-through reports, relationships, and cross-tabs in Tableau and Power BI for various clients, tailored to their specific requirements.}
        \resumeItem{Designed and maintained data visualizations to educate, inform, and engage business partners on key metrics and performance measures.}
        \resumeItem{Conducted data-driven analytics to generate actionable business insights for the leadership team, communicating these insights to senior leadership.}
        \resumeItem{Developed a text analytics tool using Python, integrated it with Power BI, and produced business reports for leadership based on cross-functional data gathered via SQL.}
        \resumeItem{Developed a Time Series Analysis and Forecasting model using Python, implemented it in Tableau, achieving 82\% accuracy in volume forecasts.}
        \resumeItem{Developed a performance scorecard through Advanced Excel, VBA, and Power Query and automated the sharing of email distribution across India.}
        \resumeItem{Developed and maintained documentation for all data visualization processes and created training materials for end users. Conducted user training sessions to ensure effective utilization of reports and dashboards.}
        \resumeItem{Supervised direct reports and led projects, prioritizing tasks and ensuring timely delivery.}

    \resumeItemListEnd
    
    \resumeSubheading
    {Tata Consultancy Services}{Jun 2016 -- Mar 2019}
    {Data Analyst}{Bengaluru, Karnataka}
    \resumeItemListStart
        \resumeItem{Created comprehensive Power BI reports, involving data transformation, data modeling, DAX calculations, and publication to services. Constructed and executed dynamic reports, dashboards, and KPI scorecards using Power BI.}
        \resumeItem{Tested, cleaned, and standardized data to meet business standards. Analyzed reporting functions and efficiencies, reducing error rates and increasing efficiency by 80\% using Tableau, Advanced Excel, VBA, and UiPath.}
        \resumeItem{Collaborated with cross-functional teams to collect and analyze data, presenting findings to clients and internal stakeholders.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------%
\section{Certifications}
\begin{itemize}[leftmargin=0.35in, label=\textbullet, itemsep=0.1em]
    \item \small Hacker Rank – SQL Advanced Certification (Gold badge)
    \item \small Microsoft Certified: Power BI Data Analyst Associate (PL-300)
    \item \small Microsoft Certified: Azure AI Fundamentals (AI-900)
    \item \small Microsoft Certified: Azure Data Fundamentals (DP-900)
    \item \small Lean Six Sigma Green Belt Certification
\end{itemize}


%-----------EDUCATION-----------%
\section{Education}
    \resumeSubHeadingListStart

    \resumeSubheading
    {Post Graduate in Data Science and Business Analytics}{}
    {Great Lakes Institute of Management}{}

    \resumeItemListStart
       \resumeItem{\textbf{Relevant Coursework:}  Python, Advanced Statistics, Data Mining, Predictive Modelling, Machine Learning, Time Series Forecasting, SQL, Marketing \& Retail Analytics, SAS}
    \resumeItemListEnd

    \resumeSubheading
    {Bachelor’s degree in Commerce (PA)}{}
    {Shri Nehru Maha Vidyalaya, Bharathiar University}{}
    \resumeItemListStart
        {}
    \resumeItemListEnd
    
    \resumeSubheading
    {HSC}{}
    {PMG Matriculation Higher Sec school}{}
    
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------%
%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Liquidity Prediction} $|$ \emph{Exploratory Data Analysis, Exponential Smoothing, ARIMA/SARIMA \& Moving Average Models, Tableau}}{}
    \resumeItemListStart
        \resumeItem {Analyzed historical monthly data to create forecast models identifying future liquidity needs for each country. Recommended the optimal model for predicting monthly sales over the next 12 months, including appropriate lower and upper confidence limits.}
        \resumeItem{Designed multiple models for each country to identify and analyze the most accurate model for each specific country.}
        \resumeItem{Integrated the model outputs into Tableau to present the findings to senior management.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Invoices Paid on Time Prediction} $|$ \emph{Exploratory Data Analysis, Linear Regression, LDA, Ensemble Techniques, Tableau}}{}
    \resumeItemListStart
        \resumeItem{Utilized a predictive model to analyze historical data and forecast current month data, identifying invoices likely to default for each customer and presented the insights to the management using Tableau}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Bank Customer Segmentation and Insurance Claim Prediction} $|$ \emph{EDA, Clustering, Random Forest, CART, Power BI}}{}
    \resumeItemListStart
        \resumeItem{The project involved drawing inferences from 2 case studies, namely - Bank Marketing \& Insurance. The concepts of Clustering, CART, Random Forest, Artificial Neural Network are used to draw inferences from these case studies. Various performance metrics have been used to validate the performance of predictions on Test \& Train sets and visualized using Power BI.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------------------------------%
\end{document}